\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

\setmainfont{EB Garamond}[Ligatures=TeX]

\definecolor{accent}{HTML}{2B2B2B}
\definecolor{muted}{HTML}{707070}

\setlist[itemize]{leftmargin=1.1em, topsep=2pt, itemsep=2pt, parsep=0pt}
\titleformat{\section}{\large\itshape\color{accent}}{}{0pt}{}[\vspace{-3pt}\rule{2cm}{0.4pt}]
\titlespacing*{\section}{0pt}{14pt}{6pt}

\pagestyle{empty}

\begin{document}

\begin{center}
{\huge Marcelo Vironda Rozanti}\\[3pt]
{\itshape\color{muted} software, written carefully}\\[3pt]
{\small mvrozanti@hotmail.com · São Paulo, BR · github.com/mvrozanti · mvrozanti.github.io}
\end{center}

\section*{}

I write backend software, mostly on the JVM. I have done that for nine years inside Brazilian fintech -- banks, payments, fiscal automation -- and I keep doing it because the systems are interesting and the consequences are real. Outside work I write small tools that I want to exist. Some of them got popular.

\section{Selected open source}

\noindent\textbf{RAT-via-Telegram} -- Windows remote administration over Telegram. 600+ stars.\\
{\small\color{muted}\url{https://github.com/mvrozanti/RAT-via-Telegram}}
\par\medskip

\noindent\textbf{dte} -- A small language for date \& time, because GNU \texttt{date} is a punishment. 300+ stars.\\
{\small\color{muted}\url{https://github.com/mvrozanti/dte}}
\par\medskip

\noindent\textbf{yawc} -- Yet Another WhatsApp Client. A long experiment in scripting a chat client that wasn't meant to be scripted.\\
{\small\color{muted}\url{https://github.com/mvrozanti/yawc}}
\par\medskip

\noindent\textbf{dotty} -- A dotfiles manager from before I migrated to Nix.\\
{\small\color{muted}\url{https://github.com/mvrozanti/dotty}}

\section{Day job}

\noindent\textbf{Senior Engineer · C6 Bank} \hfill 04/2025 -- present\\
Critical credit-granting services. Kotlin, Spring, Mongo, Postgres, Docker. Domain-driven, observability-first.

\medskip
\noindent\textbf{Software Engineer · Fiserv} \hfill 03/2024 -- 04/2025\\
POS platform. Led DevSecOps adoption -- Fortify, Sonar, CyberArk in CI. Owned disaster prevention and recovery posture.

\medskip
\noindent\textbf{Backend Developer · Conta Azul} \hfill 09/2021 -- 08/2022\\
Built the automation that took Brazilian fiscal obligations (SPED, eSocial, EFD-Reinf) off humans. AWS, Terraform.

\medskip
\noindent\textbf{Backend Developer · Grão} \hfill 12/2020 -- 09/2021\\
Implemented the Pix instant-payment backend in Kotlin, from spec to launch.

\medskip
\noindent\textbf{Developer · Raia Drogasil} \hfill 01/2020 -- 12/2020\\
LGPD-compliance retrofit of selling-operations software. Biometric and thermal-printer hardware integration.

\medskip
\noindent\textbf{Developer · Sys4Bank} \hfill 03/2016 -- 01/2020\\
Banking back-office on Spring Boot. First production-grade exposure; introduced containers and Travis CI.

\section{Skills}

\noindent
Languages I reach for daily: Kotlin, Java, Python, Shell.\\
Frameworks I know well: Spring, Spring Boot, Javalin, Koin.\\
Databases I have shipped: Postgres, Mongo, MySQL, Oracle, MSSQL, Redis.\\
Platform: Docker, AWS, Terraform, GitLab CI, Harness, Linux (daily since 2009).\\
Spoken: Portuguese (native), English (fluent), Spanish (intermediate).

\section{Education}

B.Sc.\ Computer Science -- Universidade Presbiteriana Mackenzie, São Paulo (2020).\\
Dissertation on asynchronous update schedules in elementary cellular automata. I still think about cellular automata more than I should.

\end{document}
