\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=1.7cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

\setmainfont{Lato}

\definecolor{accent}{HTML}{0B3D2E}
\definecolor{muted}{HTML}{606060}

\setlist[itemize]{leftmargin=1em, topsep=2pt, itemsep=2pt, parsep=0pt}
\titleformat{\section}{\large\bfseries\color{accent}\MakeUppercase}{}{0pt}{}[\vspace{-3pt}\rule{\linewidth}{0.5pt}]
\titlespacing*{\section}{0pt}{10pt}{5pt}

\pagestyle{empty}

\begin{document}

\begin{center}
{\Huge\bfseries Marcelo Vironda Rozanti}\\[2pt]
{\large\color{accent} Backend Engineer · Systems-level thinking · Staff trajectory}\\[3pt]
{\small mvrozanti@hotmail.com · São Paulo, BR · linkedin.com/in/mvrozanti · github.com/mvrozanti · mvrozanti.github.io}
\end{center}

\section{Positioning}
9+ years building production backend systems for regulated Brazilian fintech. I am at my best when the problem is one rung above "implement this endpoint" -- defining service boundaries, choosing how state moves, deciding what fails how, making the observability and recovery story coherent. Currently a senior IC; targeting staff / architect roles where breadth-of-system is the work.

\section{Where I add value}
\begin{itemize}
\item \textbf{Service boundaries \& domain modeling.} DDD applied as a tool, not a religion -- bounded contexts, integration patterns, ubiquitous-language hygiene where it matters.
\item \textbf{Operability as design input.} Observability, idempotency, retries, recovery, secrets -- decided at design time, not patched in later.
\item \textbf{Cross-team leverage.} Codified runbooks, durable docs, security gates in CI -- the kind of work that survives team rotation.
\item \textbf{Production credibility.} Years on-call across credit decisioning, payments, card-present, fiscal automation. The systems I design are systems I would carry the pager for.
\end{itemize}

\section{Selected work}

\noindent\textbf{Credit-Granting Platform · C6 Bank} \hfill 04/2025 -- present
\begin{itemize}
\item Designed and owns critical credit-decision services at top-tier Brazilian digital bank.
\item DDD across credit-decision domains; observability, idempotency, recovery as first-class concerns.
\item Stack: Kotlin · Spring · MongoDB · PostgreSQL · Docker · Harness · Splunk · Grafana.
\end{itemize}

\noindent\textbf{POS Platform · Fiserv} \hfill 03/2024 -- 04/2025
\begin{itemize}
\item Hardened DevSecOps posture: Fortify and Sonar gating, CyberArk secrets, hardened release pipelines.
\item Owned disaster-prevention and recovery posture -- runbooks, alerting, rehearsals.
\item Stack: Spring · Oracle SQL · Docker · Splunk · Dynatrace · Mercurial · Redis.
\end{itemize}

\noindent\textbf{Fiscal Automation · Conta Azul} \hfill 09/2021 -- 08/2022
\begin{itemize}
\item Designed event-driven fiscal-obligations engine on AWS-native primitives (SQS, S3) with Terraform IaC.
\item Removed manual SPED / eSocial / EFD-Reinf workload from product surface.
\end{itemize}

\noindent\textbf{Pix Launch · Grão} \hfill 12/2020 -- 09/2021
\begin{itemize}
\item Implemented Pix instant-payment backend in Kotlin from spec through go-live.
\item Schema design driven by access patterns; containerized environments; scalable REST APIs.
\end{itemize}

\noindent\textbf{LGPD Retrofit · Raia Drogasil} \hfill 01/2020 -- 12/2020
\begin{itemize}
\item Refactored selling-operations software for LGPD compliance during enforcement window.
\item Integrated biometric readers and thermal printers into in-store stack.
\end{itemize}

\noindent\textbf{Banking Back-Office · Sys4Bank} \hfill 03/2016 -- 01/2020
\begin{itemize}
\item Spring Boot services across corporate, financial, credit and account workflows.
\item Introduced containerization and Travis CI to a previously manual deployment culture.
\end{itemize}

\section{Open source}
\noindent\textbf{RAT-via-Telegram} (★ 600+) · \textbf{dte} (★ 300+) · \textbf{yawc} · \textbf{dotty} \hfill github.com/mvrozanti

\section{Stack (depth, not bingo)}
\noindent\textbf{Primary:} Kotlin, Java, Spring \& Spring Boot, SQL, Docker, Linux\\
\textbf{Secondary:} Python, Shell, Mongo, AWS, Terraform, Kafka-adjacent messaging\\
\textbf{Spoken:} Portuguese (native), English (fluent), Spanish (intermediate)

\section{Education}
\noindent\textbf{B.Sc.\ Computer Science}, Mackenzie, São Paulo \hfill 2020\\
{\small\color{muted}Dissertation: asynchronous update schedule by neighborhood priority in elementary cellular automata.}

\end{document}
