\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper,ragged2e]{altacv}

\geometry{left=0.5cm,right=9cm,marginparwidth=6.8cm,marginparsep=1cm,top=1.25cm,bottom=1.25cm}

\ifxetexorluatex
  \setmainfont{Lato}
\else
  \usepackage[utf8]{inputenc}\usepackage[T1]{fontenc}\usepackage[default]{lato}
\fi
\usepackage{hyperref}\hypersetup{hidelinks}

\definecolor{DarkTeal}{HTML}{1F4E5F}
\definecolor{Accent}{HTML}{C9543C}
\colorlet{heading}{DarkTeal}\colorlet{accent}{DarkTeal}
\colorlet{emphasis}{Accent}\colorlet{body}{black}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\addbibresource{refs.bib}

\begin{document}
\name{Marcelo Vironda Rozanti}
\tagline{Senior Backend Engineer · JVM · Fintech}
\personalinfo{%
  \email{mvrozanti@hotmail.com}
  \location{São Paulo, Brazil}
  \homepage{mvrozanti.github.io} \\
  \linkedin{linkedin.com/in/mvrozanti}
  \github{github.com/mvrozanti}
}

\begin{fullwidth}\makecvheader\end{fullwidth}

\cvsection[sidebar]{Experience}

\cvevent{Senior Software Engineer}{\href{https://www.srmasset.com.br}{SRM Asset}}{03/2026 -- present}{São Paulo}
\begin{itemize}
\item Build backend integrations with B3 and CERC registries for Duplicatas Escriturais (book-entry trade receivables) -- a regulated Brazilian receivables-registration rail.
\item Integrate QI Tech banking- and credit-as-a-service APIs into the platform.
\item AI-accelerated delivery: RAG over regulatory and API documentation, the BMAD agile-AI workflow, and LLM best practices -- evals, structured output, guardrails, MCP tooling.
\end{itemize}
\cvtag{Java}\cvtag{Spring}\cvtag{Aurora PostgreSQL}\cvtag{AWS}\cvtag{Docker}\cvtag{MyBatis}\cvtag{RabbitMQ}\cvtag{Keycloak}\cvtag{Terraform}\cvtag{RAG}\cvtag{BMAD}\cvtag{MCP}

\divider

\cvevent{Senior Engineer}{\href{https://www.c6bank.com}{C6 Bank}}{04/2025 -- 03/2026}{São Paulo}
\begin{itemize}
\item Own design and operation of high-availability credit-granting services for one of Brazil's largest digital banks.
\item Drive domain-driven design across credit-decision domains; champion correctness, observability, and recovery patterns in production code paths.
\item Information-security posture: secrets management, least-privilege access, hardened CI/CD via Harness.
\end{itemize}
\cvtag{Kotlin}\cvtag{Spring}\cvtag{MongoDB}\cvtag{PostgreSQL}\cvtag{Docker}\cvtag{Harness}\cvtag{Grafana}\cvtag{Splunk}\cvtag{Koin/Javalin}\cvtag{DDD}

\divider

\cvevent{Software Engineer}{\href{https://www.fiserv.com}{Fiserv}}{03/2024 -- 04/2025}{São Paulo}
\begin{itemize}
\item Delivered POS-platform services across global merchant footprint; owned monitoring, alerting, and disaster-recovery posture.
\item Led DevSecOps efforts: Fortify + Sonar gating in CI/CD, CyberArk-backed secrets, hardened release pipelines.
\item Wrote durable technical and process documentation that outlasts the team rotation.
\end{itemize}
\cvtag{Spring}\cvtag{Oracle SQL}\cvtag{Docker}\cvtag{Splunk}\cvtag{Dynatrace}\cvtag{Fortify}\cvtag{Sonar}\cvtag{CyberArk}\cvtag{Redis}\cvtag{Mercurial}

\divider

\cvevent{Backend Developer}{\href{https://www.upwork.com}{Upwork}}{Sep 2022 -- Feb 2024}{Remote (Freelance)}
\begin{itemize}
\item Solo contractor serving international clients: backend services and web data-extraction / automation pipelines across diverse sources.
\item Daily English-language client communication, scoping, and delivery.
\end{itemize}
\cvtag{Python}\cvtag{lxml}\cvtag{BeautifulSoup}\cvtag{pup}\cvtag{Headless Chromium}\cvtag{PhantomJS}\cvtag{Bash}

\divider

\cvevent{Backend Engineer}{\href{https://www.contaazul.com}{Conta Azul}}{Sep 2021 -- Aug 2022}{São Paulo}
\begin{itemize}
\item Built a fiscal-obligations engine that automated periodic and ad-hoc SPED / eSocial / EFD-Reinf submissions for SMB accounting customers.
\item Ran the service on AWS-native primitives (queues, storage) with infrastructure-as-code via Terraform.
\end{itemize}
\cvtag{Java}\cvtag{Spring}\cvtag{AWS}\cvtag{Terraform}\cvtag{PostgreSQL}\cvtag{LogDNA}

\divider

\cvevent{Backend Engineer}{\href{https://www.grao.com.br}{Grão}}{Dec 2020 -- Sep 2021}{São Paulo}
\begin{itemize}
\item Implemented Pix instant-payment integration in Kotlin from kickoff through production launch -- a regulated, central-bank-mandated rail.
\item Performance-focused schema and entity modeling; container-based test and production environments.
\item Scalable REST API design with QA automation in the loop.
\end{itemize}
\cvtag{Kotlin}\cvtag{Java EE}\cvtag{Spring}\cvtag{MySQL}\cvtag{Feign}\cvtag{Firebase}\cvtag{GitLab CI}\cvtag{Graylog}\cvtag{Postman}\cvtag{Svelte}

\divider

\cvevent{Software Developer}{\href{https://www.rd.com.br}{Raia Drogasil}}{Jan 2020 -- Dec 2020}{São Paulo}
\begin{itemize}
\item Brought selling-operations software into LGPD compliance during the law's enforcement onset.
\item Integrated biometric readers and thermal printers into the in-store stack; daily Oracle modeling.
\end{itemize}
\cvtag{Java EE}\cvtag{Oracle SQL}\cvtag{JSF/PrimeFaces}\cvtag{JBoss}\cvtag{WebLogic}\cvtag{DTAP}\cvtag{TDD}

\divider

\cvevent{Software Developer}{\href{https://www.sys4bank.com.br}{Sys4Bank}}{Mar 2016 -- Jan 2020}{São Paulo}
\begin{itemize}
\item First production-grade exposure: Spring Boot services backing banking back-office.
\item Introduced containerization and Travis CI pipelines to a team coming from manual deployment.
\end{itemize}
\cvtag{Java}\cvtag{Spring Boot}\cvtag{MSSQL}\cvtag{Maven}\cvtag{Ant}\cvtag{Bash}\cvtag{Travis CI}\cvtag{Linux}

\clearpage
\end{document}
