\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{burgundy}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.82]{geometry}
\usepackage{hyperref}

\name{Marcelo}{Vironda Rozanti}
\title{Senior Backend Engineer · Banking \& Payments}
\address{Rua Piauí 163}{São Paulo - SP, Brazil}{}
\email{mvrozanti@hotmail.com}
\homepage{mvrozanti.github.io}
\social[linkedin]{mvrozanti}
\social[github]{mvrozanti}

\begin{document}
\makecvtitle

\section{Profile}
Nine years building production JVM systems for Brazilian banks, payment processors, and regulated fintech. Quiet operator; comfortable in compliance-heavy environments. Last four roles inside banking, payments, or fiscal automation.

\section{Experience}

\cventry{04/2025 -- present}{Senior Engineer}{C6 Bank}{São Paulo}{}{%
Credit-granting platform: high-availability Kotlin services, DDD, Spring, MongoDB, PostgreSQL, observability via Splunk and Grafana.}

\cventry{03/2024 -- 04/2025}{Software Engineer}{Fiserv}{São Paulo}{}{%
POS / card-present payments. DevSecOps lead: Fortify, Sonar, CyberArk in CI. Disaster prevention and recovery posture for production services.}

\cventry{09/2021 -- 08/2022}{Backend Developer}{Conta Azul}{São Paulo}{}{%
Built automation for Brazilian fiscal obligations (SPED, eSocial, EFD-Reinf). AWS, Terraform, Postgres.}

\cventry{12/2020 -- 09/2021}{Backend Developer}{Grão}{São Paulo}{}{%
Implemented Pix instant-payment backend in Kotlin. Container-based environments, scalable REST APIs.}

\cventry{01/2020 -- 12/2020}{Developer}{Raia Drogasil}{São Paulo}{}{%
LGPD-compliance retrofit of selling-operations software. Biometric and thermal-printer hardware integration.}

\cventry{03/2016 -- 01/2020}{Developer}{Sys4Bank}{São Paulo}{}{%
Banking back-office services on Spring Boot. Introduced containerization and Travis CI; MSSQL daily.}

\section{Education}
\cventry{2020}{B.Sc.\ Computer Science}{Mackenzie}{São Paulo}{}{}

\section{Selected open source}
\cvitem{}{\href{https://github.com/mvrozanti/RAT-via-Telegram}{RAT-via-Telegram} -- Windows RAT over Telegram, 600+ stars}
\cvitem{}{\href{https://github.com/mvrozanti/dte}{dte} -- date \& time processing language, 300+ stars}

\section{Languages \& spoken}
\cvitem{Stack}{Kotlin, Java, Spring/Spring Boot, SQL (Postgres, Oracle, MSSQL, Mongo), Docker, Linux, Python, Shell}
\cvitem{Spoken}{Portuguese (native), English (fluent), Spanish (intermediate)}

\end{document}
