\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=1.7cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

\setmainfont{Lato}

\definecolor{accent}{HTML}{6A4C93}
\definecolor{muted}{HTML}{606060}

\setlist[itemize]{leftmargin=1.1em, topsep=2pt, itemsep=2pt, parsep=0pt}
\titleformat{\section}{\large\bfseries\color{accent}\MakeUppercase}{}{0pt}{}[\vspace{-3pt}\rule{\linewidth}{0.5pt}]
\titlespacing*{\section}{0pt}{10pt}{5pt}

\pagestyle{empty}

\begin{document}

\begin{center}
{\Huge\bfseries Marcelo Vironda Rozanti}\\[3pt]
{\large\color{accent} Backend Engineer · Polyglot · Hands-on}\\[3pt]
{\small mvrozanti@hotmail.com · São Paulo, BR · linkedin.com/in/mvrozanti · github.com/mvrozanti · mvrozanti.github.io}
\end{center}

\section{About}
I am a backend engineer with nine years inside Brazilian fintech, but I would describe myself less by the stack and more by how I work: I pick up new languages and tools quickly, I treat the system around the code (deploy, observe, recover) as part of the work, and I default to writing the small tool rather than working around the missing one.

\section{What I have written code in}

\noindent\textbf{Daily:} Kotlin · Java · Python · Shell / Bash\\
\textbf{Shipped to production:} Java EE, Spring, Spring Boot, Javalin, Koin\\
\textbf{Comfortable:} C, C++ (mostly for tools and exploration)\\
\textbf{Have read \& touched:} Svelte, JSF / PrimeFaces, Lua (Hyprland config, Neovim), Nix (daily on NixOS)\\
\textbf{SQL dialects in production:} PostgreSQL, MySQL, Oracle, Microsoft SQL Server\\
\textbf{NoSQL in production:} MongoDB, Redis

\section{Experience}

\noindent\textbf{Senior Engineer · C6 Bank} \hfill 04/2025 -- present\\
{\small\color{muted}Kotlin · Spring · Mongo · Postgres · Docker · Harness · Splunk · Grafana · DDD}
\begin{itemize}
\item Owns design and operation of high-availability credit-granting services.
\item DDD across credit-decision domains; observability and recovery as first-class.
\end{itemize}

\noindent\textbf{Software Engineer · Fiserv} \hfill 03/2024 -- 04/2025\\
{\small\color{muted}Spring · Oracle · Docker · Splunk · Dynatrace · Fortify · Sonar · CyberArk · Redis · Mercurial}
\begin{itemize}
\item POS-platform engineering; led DevSecOps adoption.
\item Owned disaster-prevention and recovery posture.
\end{itemize}

\noindent\textbf{Backend Developer · Conta Azul} \hfill 09/2021 -- 08/2022\\
{\small\color{muted}Java · Spring · AWS · Terraform · Postgres · LogDNA}
\begin{itemize}
\item Built fiscal-obligations automation (SPED, eSocial, EFD-Reinf) on AWS.
\end{itemize}

\noindent\textbf{Backend Developer · Grão} \hfill 12/2020 -- 09/2021\\
{\small\color{muted}Kotlin · Spring · MySQL · Feign · GitLab CI · Svelte}
\begin{itemize}
\item Implemented Pix instant-payment backend in Kotlin; some Svelte on the front-end side as needed.
\end{itemize}

\noindent\textbf{Developer · Raia Drogasil} \hfill 01/2020 -- 12/2020\\
{\small\color{muted}Java EE · Oracle · JSF/PrimeFaces · JBoss · WebLogic · TDD}
\begin{itemize}
\item LGPD-compliance retrofit; biometric and thermal-printer hardware integration -- non-trivial because the hardware drivers were not Java-shaped.
\end{itemize}

\noindent\textbf{Developer · Sys4Bank} \hfill 03/2016 -- 01/2020\\
{\small\color{muted}Java · Spring Boot · MSSQL · Ant · Maven · Bash · Travis CI · Linux}
\begin{itemize}
\item Banking back-office on Spring Boot. Introduced containers and Travis CI.
\end{itemize}

\section{Open source}
\noindent
\textbf{RAT-via-Telegram} (★ 600+, Python) · \textbf{dte} (★ 300+, Python) · \textbf{yawc} (Python) · \textbf{dotty} (Bash)\\
{\small\color{muted}github.com/mvrozanti}

\section{Education}
\noindent\textbf{B.Sc.\ Computer Science}, Universidade Presbiteriana Mackenzie, São Paulo \hfill 2020\\
{\small\color{muted}Dissertation on asynchronous update in elementary cellular automata.}

\section{Spoken languages}
Portuguese (native) · English (fluent) · Spanish (intermediate)

\end{document}
