\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.82]{geometry}
\usepackage{hyperref}

\name{Marcelo}{Vironda Rozanti}
\title{Senior Backend Engineer}
\address{Rua Piauí 163}{São Paulo - SP, Brazil}{}
\email{mvrozanti@hotmail.com}
\homepage{mvrozanti.github.io}
\social[linkedin]{mvrozanti}
\social[github]{mvrozanti}

\begin{document}
\makecvtitle

\section{Summary}
JVM backend engineer with nine years in Brazilian banking and fintech. Comfortable owning critical, regulated services from design through production operation. Recent focus: credit-decision systems, instant payments, fiscal automation.

\section{Experience}

\cventry{04/2025 -- present}{Senior Engineer}{\href{https://www.c6bank.com}{C6 Bank}}{São Paulo}{}{%
Owns design, implementation and operation of high-availability credit-granting services. Domain-driven Kotlin codebase; observability and recovery patterns as first-class concerns.
\begin{itemize}
\item Kotlin, Spring, MongoDB, PostgreSQL, Docker
\item Harness CI/CD; Splunk, Grafana for observability
\end{itemize}}

\cventry{03/2024 -- 04/2025}{Software Engineer}{\href{https://www.fiserv.com}{Fiserv}}{São Paulo}{}{%
POS-platform services for card-present payments. Owned disaster-prevention and recovery posture; led DevSecOps adoption in the team.
\begin{itemize}
\item Spring, Oracle SQL, Docker, Redis
\item Splunk + Dynatrace; Fortify, Sonar, CyberArk in CI
\end{itemize}}

\cventry{09/2021 -- 08/2022}{Backend Developer}{\href{https://www.contaazul.com}{Conta Azul}}{São Paulo}{}{%
Designed and built fiscal-obligations automation (SPED, eSocial, EFD-Reinf) for SMB accounting customers. AWS-native primitives, IaC via Terraform.}

\cventry{12/2020 -- 09/2021}{Backend Developer}{\href{https://www.grao.com.br}{Grão}}{São Paulo}{}{%
Implemented Pix instant-payment integration in Kotlin from kickoff through launch. Containerized environments; performance-focused schema design; scalable REST APIs.}

\cventry{01/2020 -- 12/2020}{Developer}{\href{https://www.rd.com.br}{Raia Drogasil}}{São Paulo}{}{%
Brought selling-operations software into LGPD compliance. Integrated biometric readers and thermal printers; daily Oracle SQL modeling.}

\cventry{03/2016 -- 01/2020}{Developer}{\href{https://www.sys4bank.com.br}{Sys4Bank}}{São Paulo}{}{%
Banking back-office services on Spring Boot. Introduced containerization and Travis CI; daily MSSQL modeling.}

\section{Education}
\cventry{2020}{B.Sc.\ Computer Science}{Universidade Presbiteriana Mackenzie}{São Paulo}{}{%
Dissertation: asynchronous update schedule by neighborhood priority in elementary cellular automata.}

\section{Open source}
\cvitem{\href{https://github.com/mvrozanti/RAT-via-Telegram}{RAT-via-Telegram}}{Windows RAT over Telegram (600+ stars)}
\cvitem{\href{https://github.com/mvrozanti/dte}{dte}}{Date \& time processing language (300+ stars)}
\cvitem{\href{https://github.com/mvrozanti/dotty}{dotty}}{Dotfiles sync \& version manager}

\section{Skills}
\cvitem{Languages}{Java, Kotlin, Python, C/C++, Shell}
\cvitem{Frameworks}{Spring, Spring Boot, Javalin, Koin}
\cvitem{Data}{PostgreSQL, MongoDB, MySQL, Oracle, MSSQL, Redis}
\cvitem{Platform}{Docker, AWS, Terraform, GitLab CI, Harness, Travis CI}
\cvitem{Spoken}{Portuguese (native), English (fluent), Spanish (intermediate)}

\end{document}
