\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=1cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{paracol}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fontawesome5}

\setmainfont{Lato}
\definecolor{accent}{HTML}{1F4E5F}
\definecolor{muted}{HTML}{606060}
\hypersetup{hidelinks}

\setlist[itemize]{leftmargin=1em, topsep=0pt, itemsep=1pt, parsep=0pt}
\titleformat{\section}{\normalsize\bfseries\color{accent}\MakeUppercase}{}{0pt}{}[\vspace{-3pt}\hrule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\setlength{\columnsep}{1.2cm}
\columnratio{0.36,0.64}

\newcommand{\role}[4]{\textbf{#1}\\\textit{\color{muted}#2}\hfill\small\color{muted}#3 · #4\par\smallskip}

\begin{document}
\pagestyle{empty}

\begin{center}
{\Huge\bfseries Marcelo Vironda Rozanti}\\[2pt]
{\color{accent}\large Senior Backend Engineer · JVM · Fintech}\\[3pt]
{\footnotesize \faEnvelope\ mvrozanti@hotmail.com · \faMapMarker*\ São Paulo, BR · \faGithub\ github.com/mvrozanti · \faLinkedin\ linkedin.com/in/mvrozanti}
\end{center}
\vspace{2pt}

\begin{paracol}{2}

\section{Summary}
\small Nine years of production JVM engineering inside Brazilian banking, payments and regulated fintech. Owns critical services end-to-end. Recent depth: credit decisioning, Pix, POS / acquirer, fiscal automation.

\section{Skills}
\footnotesize
\textbf{Lang:} Kotlin, Java, Python, Shell, C/C++ \\
\textbf{JVM:} Spring, Spring Boot, Javalin, Koin \\
\textbf{Data:} Postgres, Mongo, MySQL, Oracle, MSSQL, Redis \\
\textbf{Platform:} Docker, AWS, Terraform, GitLab CI, Harness, Linux \\
\textbf{Observe:} Splunk, Grafana, Dynatrace, Graylog \\
\textbf{Security:} Fortify, Sonar, CyberArk \\
\textbf{Spoken:} PT (native), EN (fluent), ES (intermediate)

\section{Open source}
\footnotesize
\textbf{\href{https://github.com/mvrozanti/RAT-via-Telegram}{RAT-via-Telegram}} \hfill \faStar\ 600+\\Windows RAT over Telegram\par\smallskip
\textbf{\href{https://github.com/mvrozanti/dte}{dte}} \hfill \faStar\ 300+\\Date \& time DSL\par\smallskip
\textbf{\href{https://github.com/mvrozanti/yawc}{yawc}}\\WhatsApp client experiment\par\smallskip
\textbf{\href{https://github.com/mvrozanti/dotty}{dotty}}\\Dotfiles sync \& versioning

\section{Education}
\footnotesize \textbf{B.Sc.\ Computer Science}\\Mackenzie · 2020\\\color{muted}\scriptsize Dissertation on asynchronous update in elementary cellular automata.

\switchcolumn

\section{Experience}
\footnotesize

\role{Senior Engineer}{C6 Bank}{04/2025 -- present}{São Paulo}
\begin{itemize}
\item Owns design + operation of high-availability credit-granting services.
\item DDD codebase; observability \& recovery as first-class concerns.
\item Kotlin · Spring · Mongo · Postgres · Docker · Harness · Splunk · Grafana.
\end{itemize}\smallskip

\role{Software Engineer}{Fiserv}{03/2024 -- 04/2025}{São Paulo}
\begin{itemize}
\item POS-platform engineering at acquirer scale.
\item Led DevSecOps: Fortify + Sonar + CyberArk in CI; hardened release pipeline.
\item Owned disaster-prevention \& recovery posture.
\item Spring · Oracle · Docker · Splunk · Dynatrace · Redis · Mercurial.
\end{itemize}\smallskip

\role{Backend Engineer}{Conta Azul}{09/2021 -- 08/2022}{São Paulo}
\begin{itemize}
\item Built fiscal-obligations automation (SPED, eSocial, EFD-Reinf) for SMB accounting customers.
\item AWS-native; Terraform IaC; Postgres.
\end{itemize}\smallskip

\role{Backend Engineer}{Grão}{12/2020 -- 09/2021}{São Paulo}
\begin{itemize}
\item Implemented Pix instant-payment backend in Kotlin from kickoff through launch.
\item Containerized environments; performance-focused schema; scalable REST APIs.
\item Java EE · Kotlin · MySQL · Spring · Feign · Firebase · GitLab CI · Graylog.
\end{itemize}\smallskip

\role{Developer}{Raia Drogasil}{01/2020 -- 12/2020}{São Paulo}
\begin{itemize}
\item Brought selling-operations software into LGPD compliance.
\item Integrated biometric readers and thermal printers; daily Oracle modeling.
\item Java EE · JSF/PrimeFaces · JBoss · WebLogic · Oracle · DTAP · TDD.
\end{itemize}\smallskip

\role{Developer}{Sys4Bank}{03/2016 -- 01/2020}{São Paulo}
\begin{itemize}
\item Banking back-office on Spring Boot; corporate, financial, credit and account workflows.
\item Introduced containerization and Travis CI; MSSQL daily.
\item Java · Spring Boot · MSSQL · Maven · Ant · Bash · Linux.
\end{itemize}

\end{paracol}

\end{document}
