\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=1cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{paracol}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}

\setmainfont{Lato}

\definecolor{accent}{HTML}{0D5C63}
\definecolor{muted}{HTML}{606060}

\setlist[itemize]{leftmargin=0.9em, topsep=0pt, itemsep=1pt, parsep=0pt}
\titleformat{\section}{\small\bfseries\color{accent}\MakeUppercase}{}{0pt}{}[\vspace{-2pt}\rule{\linewidth}{0.4pt}]
\titlespacing*{\section}{0pt}{6pt}{3pt}

\setlength{\columnsep}{0.8cm}
\columnratio{0.32,0.68}

\newcommand{\role}[3]{\textbf{#1}\\\textit{\color{muted}#2}\hfill\footnotesize\color{muted}#3\par}

\pagestyle{empty}

\begin{document}

\noindent
\begin{minipage}{0.7\linewidth}
{\Huge\bfseries Marcelo Vironda Rozanti}\\[2pt]
{\large\color{accent}Senior Backend Engineer · JVM · Fintech · SRE-leaning}
\end{minipage}\hfill
\begin{minipage}{0.28\linewidth}
\footnotesize\raggedleft
\faEnvelope\ mvrozanti@hotmail.com\\
\faMapMarker*\ São Paulo, BR\\
\faGithub\ github.com/mvrozanti\\
\faLinkedin\ linkedin.com/in/mvrozanti
\end{minipage}
\vspace{6pt}

\begin{paracol}{2}

\section{Profile}
\footnotesize Nine years on JVM in regulated Brazilian fintech. Owns critical services end-to-end. Recent focus: credit decisioning, instant payments, fiscal automation, POS / acquirer.

\section{Core stack}
\footnotesize
\textbf{Lang} Kotlin, Java, Python, Shell, C/C++\\
\textbf{JVM} Spring, Spring Boot, Javalin, Koin\\
\textbf{Data} Postgres, Mongo, MySQL, Oracle, MSSQL, Redis\\
\textbf{Platform} Docker, AWS, Terraform, GitLab CI, Harness, Linux\\
\textbf{Observe} Splunk, Grafana, Dynatrace, Graylog\\
\textbf{Security} Fortify, Sonar, CyberArk

\section{Spoken}
\footnotesize Portuguese (native)\\English (fluent)\\Spanish (intermediate)

\section{Education}
\footnotesize\textbf{B.Sc.\ Computer Science}\\Mackenzie · 2020

\section{Open source}
\footnotesize
\textbf{\href{https://github.com/mvrozanti/RAT-via-Telegram}{RAT-via-Telegram}} \hfill ★600+\\
Windows RAT over Telegram\par
\smallskip
\textbf{\href{https://github.com/mvrozanti/dte}{dte}} \hfill ★300+\\Date \& time DSL\par
\smallskip
\textbf{\href{https://github.com/mvrozanti/yawc}{yawc}}\\WhatsApp client experiment\par
\smallskip
\textbf{\href{https://github.com/mvrozanti/dotty}{dotty}}\\Dotfiles versioning

\switchcolumn

\section{Experience}
\footnotesize

\role{Senior Engineer}{C6 Bank · São Paulo}{04/2025 -- present}
\begin{itemize}
\item HA credit-granting platform. Kotlin/Spring; Mongo+Postgres; Docker; Harness pipeline.
\item DDD across credit-decision domains; observability via Splunk+Grafana.
\end{itemize}
\medskip

\role{Software Engineer}{Fiserv · São Paulo}{03/2024 -- 04/2025}
\begin{itemize}
\item POS platform. Led DevSecOps adoption: Fortify+Sonar gating, CyberArk secrets, hardened CI/CD on Mercurial flows.
\item Owned disaster-prevention \& recovery posture; codified runbooks, alerting, rehearsals.
\end{itemize}
\medskip

\role{Backend Developer}{Conta Azul · São Paulo}{09/2021 -- 08/2022}
\begin{itemize}
\item Designed event-driven fiscal-obligations engine (SPED, eSocial, EFD-Reinf) on AWS SQS/S3.
\item Terraform IaC; Postgres; Java/Spring; LogDNA observability.
\end{itemize}
\medskip

\role{Backend Developer}{Grão · São Paulo}{12/2020 -- 09/2021}
\begin{itemize}
\item Implemented Pix instant-payment backend in Kotlin, spec to launch.
\item Containerized envs; access-pattern-first schemas; scalable REST APIs.
\item Java EE/Kotlin/Spring/MySQL/Feign/GitLab CI/Graylog.
\end{itemize}
\medskip

\role{Developer}{Raia Drogasil · São Paulo}{01/2020 -- 12/2020}
\begin{itemize}
\item Brought selling-operations software into LGPD compliance.
\item Integrated biometric readers and thermal printers; daily Oracle.
\item Java EE/JSF-PrimeFaces/JBoss/WebLogic/DTAP/TDD.
\end{itemize}
\medskip

\role{Developer}{Sys4Bank · São Paulo}{03/2016 -- 01/2020}
\begin{itemize}
\item Banking back-office services on Spring Boot.
\item Introduced containerization and Travis CI; daily MSSQL.
\end{itemize}

\end{paracol}

\end{document}
