\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=1.5cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

\setmainfont{Lato}

\definecolor{accent}{HTML}{1565C0}
\definecolor{muted}{HTML}{606060}

\setlist[itemize]{leftmargin=1em, topsep=2pt, itemsep=2pt, parsep=0pt}
\titleformat{\section}{\large\bfseries\color{accent}\MakeUppercase}{}{0pt}{}[\vspace{-3pt}\rule{\linewidth}{0.5pt}]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\pagestyle{empty}

\begin{document}

\begin{center}
{\Huge\bfseries Marcelo Vironda Rozanti}\\[2pt]
{\large\color{accent} Senior Backend Engineer}\\[3pt]
{\small mvrozanti@hotmail.com · São Paulo, BR · linkedin.com/in/mvrozanti · github.com/mvrozanti · mvrozanti.github.io}
\end{center}

\section{Profile}
9+ years building production backend systems on the JVM (Kotlin / Java + Spring) for regulated Brazilian fintech. Owns critical services end-to-end -- design through operation. Recent depth: credit decisioning, instant payments, fiscal automation, POS / acquirer.

\section{Experience}

\noindent\textbf{C6 Bank} — Senior Software Engineer \hfill 04/2025 -- present\\
{\small\color{muted}Kotlin · Spring · Mongo · Postgres · Docker · Harness · Splunk · Grafana · DDD}
\begin{itemize}
\item Designed and shipped high-availability credit-granting services by owning architecture, implementation, and on-call rotation, improving the team's confidence in deploying to production credit paths.
\item Drove domain-driven design across credit-decision domains by extracting bounded contexts and tightening service boundaries, reducing cross-team coupling on shared models.
\item Hardened the release pipeline by introducing security gates and secrets-management discipline in Harness, raising the security posture of every shipped change.
\end{itemize}

\noindent\textbf{Fiserv} — Software Engineer \hfill 03/2024 -- 04/2025\\
{\small\color{muted}Spring · Oracle SQL · Docker · Splunk · Dynatrace · Fortify · Sonar · CyberArk · Redis · Mercurial}
\begin{itemize}
\item Led DevSecOps adoption on the POS platform by introducing Fortify and Sonar gating plus CyberArk-backed secrets, eliminating ad-hoc credential handling from the release flow.
\item Owned disaster-prevention and recovery posture for production card-present services by codifying runbooks, alerting rules, and rehearsal procedures, reducing the team's MTTR exposure on incident scenarios.
\item Hardened CI / CD over Mercurial flows by introducing pipeline gates, audit trails, and reproducible builds, removing manual approval bottlenecks.
\end{itemize}

\noindent\textbf{Conta Azul} — Backend Developer \hfill 09/2021 -- 08/2022\\
{\small\color{muted}Java · Spring · AWS · Terraform · PostgreSQL · LogDNA}
\begin{itemize}
\item Automated periodic and ad-hoc Brazilian fiscal submissions (SPED, eSocial, EFD-Reinf) by designing an event-driven engine on AWS SQS and S3, removing manual work from the accounting product surface.
\item Codified infrastructure as Terraform modules, enabling reproducible provisioning of fiscal-automation environments across non-prod and prod.
\end{itemize}

\noindent\textbf{Grão} — Backend Developer \hfill 12/2020 -- 09/2021\\
{\small\color{muted}Kotlin · Java EE · Spring · MySQL · Feign · GitLab CI · Graylog}
\begin{itemize}
\item Implemented Brazilian Pix instant-payment backend in Kotlin by integrating with the central-bank-mandated rail from spec to launch, putting Grão on the Pix map at go-live.
\item Designed performance-conscious schemas and REST APIs by modeling access patterns first, enabling throughput-stable behavior under load.
\item Containerized test and production environments by introducing Docker-based pipelines, replacing snowflake-host development.
\end{itemize}

\noindent\textbf{Raia Drogasil} — Software Developer \hfill 01/2020 -- 12/2020\\
{\small\color{muted}Java EE · Oracle SQL · JSF/PrimeFaces · JBoss · WebLogic · DTAP · TDD}
\begin{itemize}
\item Brought selling-operations software into LGPD compliance by retrofitting data-handling code paths during the law's enforcement window, closing the gap to the new data-protection bar.
\item Integrated biometric readers and thermal printers into the in-store stack by writing hardware-specific Java drivers and integration layers.
\end{itemize}

\noindent\textbf{Sys4Bank} — Software Developer \hfill 03/2016 -- 01/2020\\
{\small\color{muted}Java · Spring Boot · MSSQL · Maven · Ant · Bash · Travis CI · Linux}
\begin{itemize}
\item Introduced containerization and Travis CI by replacing manual deployment with reproducible pipelines, reducing release toil for a banking-back-office team.
\item Built Spring Boot services backing corporate, financial, credit, and account workflows.
\end{itemize}

\section{Open source}
\textbf{RAT-via-Telegram} (600+ ★) — Windows RAT over Telegram \quad
\textbf{dte} (300+ ★) — Date/time DSL \quad
\textbf{yawc} — WhatsApp client \quad
\textbf{dotty} — Dotfiles manager \quad
\textit{github.com/mvrozanti}

\section{Education}
\noindent\textbf{B.Sc.\ Computer Science}, Universidade Presbiteriana Mackenzie, São Paulo \hfill 2020

\section{Skills}
\textbf{Languages:} Kotlin, Java, Python, Shell, C/C++ \quad
\textbf{JVM:} Spring, Spring Boot, Javalin, Koin \quad
\textbf{Data:} Postgres, Mongo, MySQL, Oracle, MSSQL, Redis \quad
\textbf{Platform:} Docker, AWS, Terraform, GitLab CI, Harness, Linux \quad
\textbf{Spoken:} PT (native), EN (fluent), ES (intermediate)

\end{document}
