\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper,ragged2e]{altacv}

\geometry{left=0.5cm,right=9cm,marginparwidth=6.8cm,marginparsep=1cm,top=1.25cm,bottom=1.25cm}

\ifxetexorluatex
  \setmainfont{Lato}
\else
  \usepackage[utf8]{inputenc}\usepackage[T1]{fontenc}\usepackage[default]{lato}
\fi
\usepackage{hyperref}\hypersetup{hidelinks}

\definecolor{Mulberr}{HTML}{72243D}
\definecolor{SlateGrey}{HTML}{9E2E2E}
\definecolor{LightGrey}{HTML}{000000}
\colorlet{heading}{black}\colorlet{accent}{Mulberr}
\colorlet{emphasis}{SlateGrey}\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\addbibresource{refs.bib}

\begin{document}
\name{Marcelo Vironda Rozanti}
\tagline{Backend Developer}
\personalinfo{%
  \email{mvrozanti@hotmail.com}
  \location{Rua Piauí 163 São Paulo - SP, Brazil}
  \homepage{mvrozanti.github.io} \\
  \linkedin{linkedin.com/in/mvrozanti}
  \github{github.com/mvrozanti}
}

\begin{fullwidth}\makecvheader\end{fullwidth}

\cvsection[sidebar]{Experience}

\cvevent{Senior Engineer}{\href{https://www.c6bank.com}{C6 Bank}}{04/2025 -- present}{São Paulo}
Responsible for designing, implementing and maintaining high-availability, performant critical systems, with information security for credit granting.
\cvtag{MongoDB}\cvtag{PostgreSQL}\cvtag{Splunk}\cvtag{Kotlin}\cvtag{Harness}\cvtag{Spring Framework}\cvtag{Docker}\cvtag{Grafana}\cvtag{Koin/Javalin}\cvtag{Domain-Driven Design}

\divider

\cvevent{Web Developer}{\href{https://www.fiserv.com}{Fiserv}}{03/2024 -- 04/2025}{São Paulo}
POS-related software development, support, monitoring and maintenance. Strong role in DevSecOps, CI/CD pipelines and both technical and processual documentation. Focus on disaster prevention and recovery.\\
\cvtag{Splunk}\cvtag{Dynatrace}\cvtag{Spring Framework}\cvtag{Oracle SQL Server}\\
\cvtag{Docker}\cvtag{Fortify}\cvtag{Sonar}\cvtag{Mercurial}\cvtag{CyberArk}\cvtag{GNU/Linux}\cvtag{Redis}\cvtag{ServiceNow}

\divider

\cvevent{Backend Developer}{\href{https://www.contaazul.com}{Conta Azul}}{Sep 2021 -- Aug 2022}{São Paulo}
Accounting solutions. Implemented a system to automatically manage periodic and aperiodic tax obligations related to Brazilian SPED/eSocial government modules.\\
\cvtag{Java 8/11/15/16}\cvtag{AWS}\cvtag{Terraform}\cvtag{PostgreSQL}\cvtag{LogDNA}\cvtag{Spring}

\divider

\cvevent{Backend Developer}{\href{https://www.grao.com.br}{Grão}}{Dec 2020 -- Sep 2021}{São Paulo}
Implementing the backend for the Brazilian instant payment system Pix in Kotlin. Container-based environments. Performance-focused entity modeling, scalable REST API design, QA testing.\\
\cvtag{Java EE}\cvtag{Kotlin}\cvtag{MySQL}\cvtag{GitLab CI}\cvtag{Firebase}\cvtag{Spring}\cvtag{Feign}\cvtag{Graylog}\cvtag{Postman}\cvtag{Tomcat}\cvtag{Svelte}

\divider

\cvevent{Developer}{\href{https://www.rd.com.br}{Raia Drogasil}}{Jan 2020 -- Dec 2020}{São Paulo}
Selling Operations solutions focused on Brazilian LGPD data-protection compliance. Java Applets, JSF/PrimeFaces; hardware-specific software for biometric readers and thermal printers. Daily Oracle SQL modeling.\\
\cvtag{Java EE}\cvtag{Applets}\cvtag{DTAP}\cvtag{TDD}\cvtag{Oracle SQL}\cvtag{JSF/PrimeFaces}\cvtag{JBoss}\cvtag{WebLogic}\cvtag{Spring}

\divider

\cvevent{Developer}{\href{https://www.sys4bank.com.br}{Sys4Bank}}{Mar 2016 -- Jan 2020}{São Paulo}
Bank infrastructure development. SpringBoot, containerization, CI/CD and DevOps. Automation + pipeline implementation. Daily MSSQL modeling.\\
\cvtag{git}\cvtag{Linux}\cvtag{Java}\cvtag{MSSQL}\cvtag{Ant}\cvtag{Maven}\cvtag{BPM}\cvtag{Bash}\cvtag{Travis CI}

\clearpage
\end{document}
