\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper,ragged2e]{altacv}

\geometry{left=0.5cm,right=9cm,marginparwidth=6.8cm,marginparsep=1cm,top=1.25cm,bottom=1.25cm}

\ifxetexorluatex
  \setmainfont{Lato}
\else
  \usepackage[utf8]{inputenc}\usepackage[T1]{fontenc}\usepackage[default]{lato}
\fi
\usepackage{hyperref}\hypersetup{hidelinks}

\definecolor{Navy}{HTML}{14213D}
\definecolor{Gold}{HTML}{B68E2D}
\colorlet{heading}{Navy}\colorlet{accent}{Navy}
\colorlet{emphasis}{Gold}\colorlet{body}{black}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\addbibresource{refs.bib}

\begin{document}
\name{Marcelo Vironda Rozanti}
\tagline{Backend Engineer · 9+ years in Brazilian banking \& payments}
\personalinfo{%
  \email{mvrozanti@hotmail.com}
  \location{São Paulo, Brazil}
  \homepage{mvrozanti.github.io} \\
  \linkedin{linkedin.com/in/mvrozanti}
  \github{github.com/mvrozanti}
}

\begin{fullwidth}\makecvheader\end{fullwidth}

\cvsection[sidebar]{Banking \& fintech track record}

\cvevent{Senior Engineer · Credit Granting}{\href{https://www.c6bank.com}{C6 Bank}}{04/2025 -- present}{São Paulo}
Building the systems that decide whether C6 lends, to whom, and on what terms. High-availability, security-sensitive, audit-friendly Kotlin services in a domain-driven codebase. Observability and incident-readiness are first-class.
\cvtag{Kotlin}\cvtag{Spring}\cvtag{MongoDB}\cvtag{PostgreSQL}\cvtag{Docker}\cvtag{Harness}\cvtag{Splunk}\cvtag{Grafana}\cvtag{DDD}

\divider

\cvevent{Engineer · POS Platform}{\href{https://www.fiserv.com}{Fiserv}}{03/2024 -- 04/2025}{São Paulo}
Card-present payments at acquirer scale. Owned the disaster-prevention and recovery posture for POS-facing services. Pushed DevSecOps deeper into the pipeline: Fortify + Sonar gates, CyberArk-backed secrets, Mercurial flows hardened.
\cvtag{Spring}\cvtag{Oracle SQL}\cvtag{Docker}\cvtag{Splunk}\cvtag{Dynatrace}\cvtag{Fortify}\cvtag{Sonar}\cvtag{CyberArk}\cvtag{Redis}

\divider

\cvevent{Backend Engineer · Fiscal Automation}{\href{https://www.contaazul.com}{Conta Azul}}{Sep 2021 -- Aug 2022}{São Paulo}
Built the automation that takes the most painful part of Brazilian SMB accounting -- SPED, eSocial, EFD-Reinf -- off humans. Periodic and event-driven submissions on AWS-native primitives, IaC via Terraform.
\cvtag{Java}\cvtag{Spring}\cvtag{AWS}\cvtag{Terraform}\cvtag{PostgreSQL}

\divider

\cvevent{Backend Engineer · Pix Launch}{\href{https://www.grao.com.br}{Grão}}{Dec 2020 -- Sep 2021}{São Paulo}
Joined a small team building Pix -- Brazil's central-bank-mandated instant payment rail -- from spec to launch. Kotlin services on containerized infrastructure, REST APIs designed for predictable throughput, schema choices driven by access patterns.
\cvtag{Kotlin}\cvtag{Java EE}\cvtag{Spring}\cvtag{MySQL}\cvtag{Feign}\cvtag{GitLab CI}\cvtag{Graylog}

\divider

\cvevent{Developer · LGPD Compliance}{\href{https://www.rd.com.br}{Raia Drogasil}}{Jan 2020 -- Dec 2020}{São Paulo}
LATAM's largest drugstore chain, in the year LGPD started biting. Rewrote selling-operations software to meet the new data-protection bar; integrated biometric and thermal-printer hardware in-store.
\cvtag{Java EE}\cvtag{Oracle SQL}\cvtag{JSF/PrimeFaces}\cvtag{JBoss}\cvtag{WebLogic}\cvtag{TDD}

\divider

\cvevent{Developer · Banking Back-Office}{\href{https://www.sys4bank.com.br}{Sys4Bank}}{Mar 2016 -- Jan 2020}{São Paulo}
Four years inside a banking-software house. Spring Boot services for corporate, financial, credit and account workflows. Introduced containerization and Travis CI to a previously hand-deployed stack.
\cvtag{Java}\cvtag{Spring Boot}\cvtag{MSSQL}\cvtag{Maven}\cvtag{Ant}\cvtag{Bash}\cvtag{Travis CI}

\clearpage
\end{document}
