\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=1.5cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

\setmainfont{Inter}

\definecolor{accent}{HTML}{FB5607}
\definecolor{muted}{HTML}{606060}

\setlist[itemize]{leftmargin=1em, topsep=2pt, itemsep=1pt, parsep=0pt}
\titleformat{\section}{\normalsize\bfseries\color{accent}\MakeUppercase}{}{0pt}{}[\vspace{-3pt}\rule{\linewidth}{0.5pt}]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\pagestyle{empty}

\begin{document}

\begin{center}
{\Huge\bfseries Marcelo Vironda Rozanti}\\[2pt]
{\large\color{accent} Backend Engineer · Builder · Wears many hats}\\[3pt]
{\small mvrozanti@hotmail.com · São Paulo · github.com/mvrozanti · mvrozanti.github.io · linkedin.com/in/mvrozanti}
\end{center}

\section{What I want}
A small team that ships. I am happiest when the work spans design, code, infra, observability, and a bit of customer empathy -- with nobody to hand the rest of the loop off to. Nine years inside Brazilian fintech taught me how to make things that hold up; I would like to apply that to a smaller stage.

\section{What I bring}
\begin{itemize}
\item \textbf{End-to-end ownership.} I have shipped Kotlin / Java / Spring backends from spec to production at C6 Bank, Fiserv, Conta Azul, Grão, and earlier.
\item \textbf{Infra fluency.} Docker, AWS, Terraform, GitLab CI, Harness. Linux is a daily driver since 2009.
\item \textbf{Comfortable past my home stack.} Python and Shell daily; touched Svelte on the front-end at Grão; OSS in Python and Bash.
\item \textbf{Builder default.} Side projects with real users: RAT-via-Telegram (600+ stars), dte (300+).
\end{itemize}

\section{Recent stops}

\noindent\textbf{C6 Bank} — Senior Engineer, credit-granting platform. Kotlin/Spring/Mongo/Postgres. \hfill 04/2025 -- now\\
\noindent\textbf{Fiserv} — POS platform; led DevSecOps adoption; owned DR posture. \hfill 03/2024 -- 04/2025\\
\noindent\textbf{Conta Azul} — Fiscal-obligations automation on AWS + Terraform. \hfill 09/2021 -- 08/2022\\
\noindent\textbf{Grão} — Implemented Pix instant-payment backend in Kotlin, spec to launch. \hfill 12/2020 -- 09/2021\\
\noindent\textbf{Raia Drogasil} — LGPD-compliance retrofit; biometric + thermal-printer integration. \hfill 01/2020 -- 12/2020\\
\noindent\textbf{Sys4Bank} — Banking back-office on Spring Boot; introduced containers + Travis CI. \hfill 03/2016 -- 01/2020

\section{Stack}
\textbf{Backend:} Kotlin, Java, Spring \& Spring Boot, Javalin, Koin \\
\textbf{Data:} Postgres, Mongo, MySQL, Oracle, MSSQL, Redis \\
\textbf{Platform:} Docker, AWS, Terraform, GitLab CI, Harness, Linux \\
\textbf{Other:} Python, Shell, C/C++; some Svelte, Lua, Nix\\
\textbf{Spoken:} Portuguese (native), English (fluent), Spanish (intermediate)

\section{Open source}
\textbf{RAT-via-Telegram} (★ 600+) · \textbf{dte} (★ 300+) · \textbf{yawc} · \textbf{dotty} \hfill github.com/mvrozanti

\section{Education}
\textbf{B.Sc.\ Computer Science}, Mackenzie, São Paulo \hfill 2020

\end{document}
