\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{green}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.82]{geometry}
\usepackage{hyperref}

\name{Marcelo}{Vironda Rozanti}
\title{Senior Backend Engineer}
\address{São Paulo, Brazil}{}{}
\email{mvrozanti@hotmail.com}
\homepage{mvrozanti.github.io}
\social[linkedin]{mvrozanti}
\social[github]{mvrozanti}

\begin{document}
\makecvtitle

\section{What I do}
I build production backend systems on the JVM -- mostly Kotlin and Java with Spring -- for companies where the cost of getting it wrong is real (banks, payment processors, fiscal automation). I have spent the last nine years inside Brazilian fintech, and I am happiest when I own a service end-to-end.

\section{Experience}

\cventry{04/2025 -- present}{Senior Engineer}{C6 Bank}{São Paulo}{}{%
Credit granting. High-availability Kotlin services on Spring + MongoDB + PostgreSQL, container-deployed via Harness; observability via Splunk and Grafana; DDD codebase.}

\cventry{03/2024 -- 04/2025}{Software Engineer}{Fiserv}{São Paulo}{}{%
POS-platform engineering. DevSecOps lead; Fortify + Sonar + CyberArk in CI; disaster prevention and recovery for production card-present services.}

\cventry{09/2021 -- 08/2022}{Backend Developer}{Conta Azul}{São Paulo}{}{%
Built fiscal-obligations automation (SPED, eSocial, EFD-Reinf) for SMB customers. AWS, Terraform IaC, Postgres.}

\cventry{12/2020 -- 09/2021}{Backend Developer}{Grão}{São Paulo}{}{%
Implemented Pix instant-payment backend in Kotlin. Containerized environments, scalable REST APIs.}

\cventry{01/2020 -- 12/2020}{Developer}{Raia Drogasil}{São Paulo}{}{%
Brought selling-operations software into LGPD compliance. Biometric and thermal-printer integration; daily Oracle.}

\cventry{03/2016 -- 01/2020}{Developer}{Sys4Bank}{São Paulo}{}{%
Banking back-office on Spring Boot. Introduced containerization and Travis CI to the team.}

\section{Open source}
\cvitem{}{\href{https://github.com/mvrozanti/RAT-via-Telegram}{RAT-via-Telegram} (600+ stars), \href{https://github.com/mvrozanti/dte}{dte} (300+ stars), \href{https://github.com/mvrozanti/dotty}{dotty}}

\section{Education}
\cventry{2020}{B.Sc.\ Computer Science}{Mackenzie}{São Paulo}{}{}

\section{Skills}
\cvitem{Core}{Kotlin, Java, Spring \& Spring Boot}
\cvitem{Data}{Postgres, Mongo, Oracle, MSSQL, Redis}
\cvitem{Platform}{Docker, AWS, Terraform, GitLab CI, Harness}
\cvitem{Other}{Python, Shell, C/C++; Linux daily}
\cvitem{Spoken}{Portuguese (native), English (fluent), Spanish (intermediate)}

\end{document}
