\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=1.5cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning,calc}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

\setmainfont{Lato}

\definecolor{accent}{HTML}{D62828}
\definecolor{spine}{HTML}{14213D}
\definecolor{muted}{HTML}{606060}

\setlist[itemize]{leftmargin=1em, topsep=2pt, itemsep=1pt, parsep=0pt}
\titleformat{\section}{\large\bfseries\color{spine}\MakeUppercase}{}{0pt}{}[\vspace{-3pt}\rule{\linewidth}{0.5pt}]
\titlespacing*{\section}{0pt}{10pt}{5pt}

\pagestyle{empty}

\newcommand{\timelineentry}[5]{%
  \begin{tikzpicture}[remember picture,baseline=(node.base)]
    \node[circle,fill=accent,inner sep=2pt] (dot) {};
    \node[right=4pt of dot, anchor=west] (node) {\textbf{#1} \textcolor{spine}{·} \textbf{#2} \hfill \textcolor{muted}{\small#3}};
  \end{tikzpicture}\par
  \hspace{0.7em}\textcolor{spine}{\vrule width 1.5pt height 0pt depth 0pt}\hspace{0.4em}\begin{minipage}[t]{0.94\linewidth}\small #4\par\vspace{1pt}\textcolor{muted}{\footnotesize #5}\end{minipage}\par\medskip
}

\begin{document}

\begin{center}
{\Huge\bfseries Marcelo Vironda Rozanti}\\[2pt]
{\large\color{accent} Senior Backend Engineer}\\[3pt]
{\small mvrozanti@hotmail.com · São Paulo, BR · linkedin.com/in/mvrozanti · github.com/mvrozanti · mvrozanti.github.io}
\end{center}

\section{Profile}
\small
Nine years of production JVM engineering inside Brazilian banking, payments, and regulated fintech. Owns critical services end-to-end. Recent focus: credit decisioning, instant payments, fiscal automation, POS / acquirer.

\section{Career timeline}

\timelineentry{C6 Bank}{Senior Engineer}{04/2025 -- present}{High-availability credit-granting services. DDD across credit-decision domains. Observability + recovery first-class.}{Kotlin · Spring · Mongo · Postgres · Docker · Harness · Splunk · Grafana}

\timelineentry{Fiserv}{Software Engineer}{03/2024 -- 04/2025}{POS-platform engineering. Led DevSecOps adoption. Owned disaster-prevention and recovery posture.}{Spring · Oracle · Docker · Splunk · Dynatrace · Fortify · Sonar · CyberArk · Redis · Mercurial}

\timelineentry{Conta Azul}{Backend Developer}{09/2021 -- 08/2022}{Built fiscal-obligations automation (SPED, eSocial, EFD-Reinf) on AWS-native primitives with Terraform IaC.}{Java · Spring · AWS · Terraform · Postgres · LogDNA}

\timelineentry{Grão}{Backend Developer}{12/2020 -- 09/2021}{Implemented Pix instant-payment backend in Kotlin from kickoff through launch. Containerized envs.}{Kotlin · Java EE · Spring · MySQL · Feign · GitLab CI · Graylog}

\timelineentry{Raia Drogasil}{Developer}{01/2020 -- 12/2020}{Brought selling-operations software into LGPD compliance. Integrated biometric / thermal-printer hardware.}{Java EE · Oracle · JSF/PrimeFaces · JBoss · WebLogic · DTAP · TDD}

\timelineentry{Sys4Bank}{Developer}{03/2016 -- 01/2020}{Banking back-office on Spring Boot. Introduced containers and Travis CI to the team.}{Java · Spring Boot · MSSQL · Maven · Ant · Bash · Travis CI · Linux}

\section{Open source}
\small\textbf{RAT-via-Telegram} (★ 600+) · \textbf{dte} (★ 300+) · \textbf{yawc} · \textbf{dotty} \hfill github.com/mvrozanti

\section{Education}
\small\textbf{B.Sc.\ Computer Science}, Universidade Presbiteriana Mackenzie, São Paulo \hfill 2020

\section{Skills \& languages}
\small
Kotlin, Java, Python, Shell, C/C++ · Spring, Spring Boot · Postgres, Mongo, MySQL, Oracle, MSSQL, Redis · Docker, AWS, Terraform, Linux\\
Portuguese (native) · English (fluent) · Spanish (intermediate)

\end{document}
