\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper,ragged2e]{altacv}

\geometry{left=0.5cm,right=9cm,marginparwidth=6.8cm,marginparsep=1cm,top=1.2cm,bottom=1.2cm}

\ifxetexorluatex
  \setmainfont{Lato}
\else
  \usepackage[utf8]{inputenc}\usepackage[T1]{fontenc}\usepackage[default]{lato}
\fi
\usepackage{hyperref}\hypersetup{hidelinks}

\definecolor{Steel}{HTML}{2C3E50}
\definecolor{Crimson}{HTML}{922B21}
\colorlet{heading}{Steel}\colorlet{accent}{Steel}
\colorlet{emphasis}{Crimson}\colorlet{body}{black}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\addbibresource{refs.bib}

\begin{document}
\name{Marcelo Vironda Rozanti}
\tagline{Backend Engineer · Regulated \& Security-Sensitive Systems}
\personalinfo{%
  \email{mvrozanti@hotmail.com}
  \location{São Paulo, Brazil}
  \homepage{mvrozanti.github.io} \\
  \linkedin{linkedin.com/in/mvrozanti}
  \github{github.com/mvrozanti}
}

\begin{fullwidth}\makecvheader\end{fullwidth}

\cvsection[sidebar]{Experience}

\cvevent{Senior Engineer · Credit Granting}{\href{https://www.c6bank.com}{C6 Bank}}{04/2025 -- present}{São Paulo}
High-availability credit-granting platform inside a top-tier Brazilian digital bank. Information-security posture as a first-class concern: secrets management, least-privilege access, hardened CI/CD via Harness. DDD codebase; auditable, observable, recoverable.
\cvtag{Kotlin}\cvtag{Spring}\cvtag{MongoDB}\cvtag{PostgreSQL}\cvtag{Docker}\cvtag{Harness}\cvtag{Splunk}\cvtag{Grafana}\cvtag{DDD}

\divider

\cvevent{Software Engineer · DevSecOps lead on POS}{\href{https://www.fiserv.com}{Fiserv}}{03/2024 -- 04/2025}{São Paulo}
POS / card-present payments platform. Led DevSecOps adoption -- Fortify and Sonar gating, CyberArk-backed secrets, hardened release pipelines. Owned disaster-prevention and recovery posture for production services.
\cvtag{Spring}\cvtag{Oracle SQL}\cvtag{Fortify}\cvtag{Sonar}\cvtag{CyberArk}\cvtag{Docker}\cvtag{Splunk}\cvtag{Dynatrace}\cvtag{Mercurial}

\divider

\cvevent{Backend Engineer · Fiscal Automation}{\href{https://www.contaazul.com}{Conta Azul}}{Sep 2021 -- Aug 2022}{São Paulo}
Automated Brazilian fiscal obligations -- SPED, eSocial, EFD-Reinf -- across periodic and ad-hoc submissions. AWS-native event-driven engine; Terraform IaC for reproducible provisioning across environments.
\cvtag{Java}\cvtag{Spring}\cvtag{AWS}\cvtag{Terraform}\cvtag{PostgreSQL}

\divider

\cvevent{Backend Engineer · Pix Launch}{\href{https://www.grao.com.br}{Grão}}{Dec 2020 -- Sep 2021}{São Paulo}
Pix instant-payment integration in Kotlin -- Brazilian central-bank-mandated rail. Spec-to-launch ownership of the backend, including container-based pipelines and access-pattern-first schema design.
\cvtag{Kotlin}\cvtag{Spring}\cvtag{MySQL}\cvtag{GitLab CI}\cvtag{Feign}

\divider

\cvevent{Developer · LGPD Compliance}{\href{https://www.rd.com.br}{Raia Drogasil}}{Jan 2020 -- Dec 2020}{São Paulo}
Brought selling-operations software into compliance with Brazilian LGPD data-protection law during the enforcement window. Retrofitted affected data-handling paths; integrated biometric readers and thermal printers.
\cvtag{Java EE}\cvtag{Oracle SQL}\cvtag{JSF/PrimeFaces}\cvtag{JBoss}\cvtag{WebLogic}\cvtag{TDD}

\divider

\cvevent{Developer · Banking Back-Office}{\href{https://www.sys4bank.com.br}{Sys4Bank}}{Mar 2016 -- Jan 2020}{São Paulo}
Banking back-office services on Spring Boot; corporate, financial, credit and account workflows. Introduced containerization and Travis CI to a previously manual deployment culture.
\cvtag{Java}\cvtag{Spring Boot}\cvtag{MSSQL}\cvtag{Maven}\cvtag{Ant}\cvtag{Travis CI}

\clearpage
\end{document}
